Implications of animal movement rate variation in spatial patterns of seed dispersal

### 2021-08-18 Ch1_movement_rates/Ch1_markdown.Rmd
Editing headlines

Now, we get the animals to disperse seeds. Seeds gut retention time are sampled from a gamma distribution.
```{r eval=FALSE}
nseeds <- 20
grt <- round(rgamma(nseeds, shape = 4, scale = 5))
t.grt <- max(grt)

@@

Run a simulation for one individual, multiple runs, display animal movement, seed dispersal and print summary for all runs
```{r message=FALSE}
nruns <- 100

for(j in 1:1){
  for(k in 1:nruns){
    a <- sim_seeds(m.prms = m_1[j]) %>% 
      mutate(indiv = as.factor(j),
             run = factor(paste0("r_", k), levels = paste0("r_", 1:nruns)))

@@

df %>% 
  ggplot(., aes(x = xloc, y = yloc)) +
  # stat_density_2d(aes(fill = ..level..), geom = "polygon", colour="white") +
  geom_bin2d() +
  # geom_hex() +
  # scale_fill_continuous(type = "viridis") +
  scale_fill_gradient(low = "grey", high = "black") +
  theme_bw() +
  theme(legend.position = "bottom") +
  labs(title = "Density of animal movement") -> p2
# p2

@@

# summ.df %>% 
#   ggplot(., aes(y = dsprsn)) +
#   geom_boxplot()
# 
# summ.df %>% 
#   ggplot(., aes(x = av.disp)) +
#   geom_density(color = "blue") + # for the average dispersal per run
#   geom_density(data = df %>% drop_na(s.id),
#                  aes(x = disp)) + # for every seed
#   theme_bw()
```

Next steps.
Fit a weibull distribution to the raw seed dispersal data, probably subsample.
Provide summary stats for the dispersal and dispersion measures.

```{r message=FALSE, warning=FALSE}
# s.df <- df %>% drop_na(s.id)

@@

g <- fitdist(s.df$disp, distr = "weibull")
summary(g)
plot(g)

>>>>

## Example individual
### Simulate movement and seed droppings

Now, we get the animals to disperse seeds. To do this, we combine seed gut retention times and animal movement. We can visualize this for one individual. Each simulation run consists of the animal disperser starting at point (0,0) and getting a number of seeds, each of which has an associated gut retention time $(grt \sim Gamma(4,5))$. The simulation run ends once all seeds have dropped. For that run, we calculate the average seed location by taking the average of x and y coordinates of all seeds. We also calculate seed dispersion as a measure of how close to each other or how scattered the seeds are for that run.
```{r eval=FALSE}
nseeds <- 20
grt <- round(rgamma(nseeds, shape = 4, scale = 5))
t.grt <- max(grt)

@@

```{r message=FALSE}
nruns <- 100
ex.i <- 1
df <- NULL
summ.df <- NULL

for(j in 1:ex.i){
  for(k in 1:nruns){
    a <- sim_seeds(m.prms = m_1[j]) %>% 
      mutate(indiv = as.factor(j),
             run = factor(paste0("r_", k), levels = paste0("r_", 1:nruns)))

@@

df %>% 
  ggplot(., aes(x = xloc, y = yloc)) +
  # stat_density_2d(aes(fill = ..level..), geom = "polygon", colour="white") +
  geom_bin2d() +
  # geom_hex() +
  # scale_fill_continuous(type = "viridis") +
  scale_fill_gradient(low = "grey", high = "black") +
  # geom_point(data = df %>% drop_na(s.id), 
  #            aes(x = xloc, y = yloc), color = mycols[ex.i], alpha = 0.3) +
  # geom_point(data = summ.df, aes(x = x, y=y), color = "black") +
  theme_bw() +
  theme(legend.position = "bottom") +
  labs(title = "Density of animal movement") -> p2
# p2

@@

# summ.df %>% 
#   ggplot(., aes(y = dsprsn)) +
#   geom_boxplot()
# 
# summ.df %>% 
#   ggplot(., aes(x = av.disp)) +
#   geom_density(color = "blue") + # for the average dispersal per run
#   geom_density(data = df %>% drop_na(s.id),
#                  aes(x = disp)) + # for every seed
#   theme_bw()
```
### Fit distribution function to seed dispersal data
The end goal here is to understand how variation in animal movement rates can impact seed dispersal patterns. To get a metric of this seed dispersal, we fit a weibull distribution to the seed dispersal data generated by the previous simulation. Every run has 20 seeds, and we did this 100 times, thus we randomly sample 50 seeds to fit a Weibull distribution and get an approximated seed dispersal kernel.

```{r message=FALSE, warning=FALSE, echo=FALSE, results='hide'}
# s.df <- df %>% drop_na(s.id)

@@

g <- fitdist(s.df$disp, distr = "weibull")
```

```{r}
summary(g)
plot(g)
